Manual of comparing optimal subsampling with model robust optimal subsampling method for poisson regression (standardised Multivariate Normal distribution)

### 2023-03-05 Manual.Rmd
Manual updated after removing classical folder from the chain

* The sub-sampling methods applied in this study are 
1. Random Sampling, 
2. Rare event random sampling, 
3. Optimal Sub-sampling (OSMAC), and
4. Model Robust Optimal Sub-sampling (OSMAC_MF or OSMAC Model Free).

@@

### 2.2.1 Classical/R_Scripts

@@

* Data stored in **Generate_Big_Data** is transferred to **Classical/Analysis**.

@@

#### 2.2.1.3 RE Random_Sampling_Setup.R

* A setup for rare event random sampling such that model parameters and model information are estimated at each simulation and are applied for the generated big data.

#### 2.2.1.4 OSMAC_Algorithm.R and OSMAC_Setup.R [Identical r0]

@@

#### 2.2.1.5 OSMAC_Algorithm.R and OSMAC_Setup.R [Non Identical r0]

@@

#### 2.2.1.6 OSMAC_Algorithm_Model_Free.R and OSMAC_Model_Free_Setup.R [Non_Identical_r0]

@@

## 2.2.2 Classical/Analysis

@@

#### 2.2.2.2 RE Random Sampling

* **Init.RData** - data file containing the generated big data and initial information regarding the simulation.
* **RE_RandomSample.RData** - RE Random sampling function for **Replicates**.
* **Simulation_Results_RE_Random_Sampling.R** - R script to run the rare event random sampling method over **Replicates** on the **Init.RData** from **RE_RandomSample.RData**.
* **Results** - Results of the simulation are stored here according to real and assumed models, in each folder a single Rdata file **RE_Random_Sample_output.RData** is stored.

#### 2.2.2.3 OSMAC [Non Identical r0]

@@

#### 2.2.2.4 OSMAC Model Free [Non Identical r0]

@@

#### 2.2.2.5 OSMAC [Identical r0]

@@

* **RE_and_Random_Sampling_and_OSMAC.R** - R script to summarise the results from the sub-sampling methods through the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd**.

@@

* **Summary_Rmarkdown.R** in the **Rmarkdown/Classical/Summary** folder compares the sub-sampling methods through Mean Squared Error, variance and model information through the **Best_Subsampling_Method.Rmd**.

@@

* Here, summaries from the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd**(for Identical and Non Identical r0) and **OSMAC_Model_Free_Method.Rmd** (for Non Identical r0) are stored as html files.

@@

### 2.6.1 Summary/Classical/Model_[1 or 2 or 3 or 4]/Data/Efficiency

* When running the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd** summary data (MSE and model information) are stored here.

* Using these data files only summarising through the files in **Rmarkdown/Classical/Summary** occurs.

@@

* Use **Articles.Rmd** to generate plots relevant to the paper as pdf files **SMSE_MI_PR_TV_Nor_mMSE.pdf** and **SMSE_MI_PR_TV_Nor_mVc.pdf**.

>>>>

* The sub-sampling methods applied in this study are 
1. Random Sampling, 
2. Optimal Sub-sampling (OSMAC), and
3. Model Robust Optimal Sub-sampling (OSMAC_MF or OSMAC Model Free).

@@

### 2.2.1 R_Scripts

@@

* Data stored in **Generate_Big_Data** is transferred to **Analysis**.

@@

#### 2.2.1.3 OSMAC_Algorithm.R and OSMAC_Setup.R [Identical r0]

@@

#### 2.2.1.4 OSMAC_Algorithm.R and OSMAC_Setup.R [Non Identical r0]

@@

#### 2.2.1.5 OSMAC_Algorithm_Model_Free.R and OSMAC_Model_Free_Setup.R [Non_Identical_r0]

@@

## 2.2.2 Analysis

@@

#### 2.2.2.2 OSMAC [Non Identical r0]

@@

#### 2.2.2.3 OSMAC Model Free [Non Identical r0]

@@

#### 2.2.2.4 OSMAC [Identical r0]

@@

* **Random_Sampling_and_OSMAC.R** - R script to summarise the results from the sub-sampling methods through the Rmarkdown files **Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd**.

@@

* **Summary_Rmarkdown.R** in the **Rmarkdown/Summary** folder compares the sub-sampling methods through Mean Squared Error, variance and model information through the **Best_Subsampling_Method.Rmd**.

@@

* Here, summaries from the Rmarkdown files **Random_Sampling.Rmd**, **OSMAC_Method.Rmd**(for Identical and Non Identical r0) and **OSMAC_Model_Free_Method.Rmd** (for Non Identical r0) are stored as html files.

@@

### 2.6.1 Summary/Model_[1 or 2 or 3 or 4]/Data/Efficiency

* When running the Rmarkdown files **Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd** summary data (MSE and model information) are stored here.

* Using these data files only summarising through the files in **Rmarkdown/Summary** occurs.

@@

* Use **Articles.Rmd** to generate plots relevant to the paper as pdf files **Article_Plots/SMSE_MI_PR_TV_Nor_mMSE.pdf** and **Article_Plots/SMSE_MI_PR_TV_Nor_mVc.pdf**.
